### 2023-08-16 paper/sec-dis-pseudodata.tex
Update sec-dis-pseudodata.tex

 Fig.~\ref{fig:fasernu2_muon} displays the differential
 event yields per bin,  Eq.~(\ref{eq:event_yields}),
 for muon neutrinos detected at the
 FASER$\nu$ (Run III) and the AdvSND, FASER$\nu$2, and FLArE  (FPF) experiments,
 restricted
 to the DIS region defined by Eq.~(\ref{eq:DISconditions})
 and where only bins with $\ge 30$ events are retained.
 %
 Adding up the bins in each of the panels results into the numbers listed in
 Table~\ref{tab:integrated_rates}.
 %
 The clear improvement in going from the current FASER$\nu$ and SND@LHC
 experiments to the FPF ones is visible both in terms
 of the number
 of events per bin as well as for the kinematic coverage.
 %
 The FPF experiments benefit from large
 event rates for most of the region in $\lp x,Q^2\rp$ covered,
 leading to typical statistical uncertainties at the 1\% level or smaller,
 while for FASER$\nu$, SND@LHC statistical uncertainties are much larger due
 to the reduced event rates.

@@

Fig.~\ref{fig:fasernu2_muon} indicates
how the kinematic coverage of the FPF far-forward experiments reaches
$x_{\rm min}\sim \times 10^{-3}$ at small-$x$ and $Q^2_{\rm max}\sim 2\times 10^3$
at large-$Q^2$, representing an extension
of around one order of magnitude in both directions as compared to available
DIS neutrino data on nuclear targets.
%
Fig.~\ref{fig:Kin_nNNPDF30_EIC_FPF} compares
the kinematic coverage of FASER$\nu$2, FLArE, and AdvSND with that of electron-ion collisions
at the upcoming EIC~\cite{Khalek:2021ulf,AbdulKhalek:2021gbh}
and to other available hard-scattering datasets involving
nuclear targets or projectiles.
%
Specifically, we display the coverage of fixed-target neutral- and charged-current nuclear DIS,
fixed-target Drell-Yan production, and $W$, $Z$, $D$-meson, photon, and dijet
production in proton-lead collisions at the LHC entering the  nNNPDF3.0
determination~\cite{AbdulKhalek:2022fyi}.
%
The LHC neutrino experiments cover the region $x\gsim 10^{-3}$ relevant
for precision electroweak measurements at the LHC, such as the $W$-boson
mass, and for new physics measurements sensitive to the large-$x$ quarks
and antiquarks in the proton.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \includegraphics[width = 0.7\textwidth]{plots/KIN_DIS_FPF.pdf}
    \caption{The kinematic coverage in the $(x,Q^2)$ plane of muon neutrino scattering
      at FASER$\nu$(2), FLArE, and SND (see also Fig.~\ref{fig:fasernu2_muon})
      compared to that of electron-ion collisions at the EIC for the highest center-of-mass 
      energies $\sqrt{s}$ planned, as well as to the coverage of other available hard-scattering 
      datasets involving nuclear targets or projectiles.
      %
      Specifically, we display the coverage of fixed-target neutral- and charged-current nuclear DIS.
      Bins with less than $30$ events are represented by the grey dots.
      %
      \textcolor{red}{(To be replaced once AdvSND and new fluxes are available.)}
      }
    \label{fig:Kin_nNNPDF30_EIC_FPF}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

 Fig.~\ref{fig:fasernu2_muon} displays the differential
 event yields per bin,  Eq.~(\ref{eq:event_yields}),
 for muon neutrinos detected at the
 FASER$\nu$ (Run III) and the AdvSND, FASER$\nu$2, and FLArE  (FPF) experiments,
 restricted
 to the DIS region defined by Eq.~(\ref{eq:DISconditions})
 and where only bins with $\ge 30$ events are retained.
 %
 Adding up the bins in each of the panels results into the inclusive yields listed in
 Table~\ref{tab:integrated_rates}.
 %
 The clear improvement in going from the current FASER$\nu$ experiment
 to the FPF ones is visible both in terms
 of the number
 of events per bin as well as for the kinematic coverage.
 %
 The FPF experiments benefit from large
 event rates for most of the region in $\lp x,Q^2\rp$ covered,
 leading to typical statistical uncertainties at the 1\% level or smaller,
 while for FASER$\nu$ the statistical uncertainties are much larger due
 to the reduced event rates.

@@

Fig.~\ref{fig:fasernu2_muon} indicates
how the kinematic coverage of the FPF far-forward experiments reaches
$x_{\rm min}\sim 3\times 10^{-3}$ at small-$x$ and $Q^2_{\rm max}\sim 10^4$ GeV$^2$
at large-$Q^2$, representing an extension
of around one order of magnitude in both directions as compared to available
DIS neutrino data on nuclear targets.
%
Fig.~\ref{fig:Kin_nNNPDF30_EIC_FPF} compares
the kinematic coverage of FASER$\nu$2, FLArE, and AdvSND with that of electron-ion collisions
at the upcoming EIC~\cite{Khalek:2021ulf,AbdulKhalek:2021gbh}
and to other available hard-scattering datasets involving
nuclear targets or projectiles.
%
Specifically, we display the coverage of fixed-target neutral- and charged-current nuclear DIS,
fixed-target Drell-Yan production, and $W$, $Z$, $D$-meson, photon, and dijet
production in proton-lead collisions at the LHC entering the  nNNPDF3.0
determination~\cite{AbdulKhalek:2022fyi}.
%
The LHC neutrino experiments cover the region $x\gsim 10^{-3}$ relevant
for precision electroweak measurements at the LHC, such as the $W$-boson
mass, and for new physics measurements sensitive to the large-$x$ quarks
and antiquarks in the proton.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \includegraphics[width = 0.85\textwidth]{plots/KIN_DIS_FPF.pdf}
    \caption{The kinematic coverage in the $(x,Q^2)$ plane of muon-neutrino scattering
      at the FASER$\nu$, FASER$\nu$2, FLArE-100, and AdvSND experiments, see also Fig.~\ref{fig:fasernu2_muon},
      compared to that of electron-ion collisions at the EIC for the highest center-of-mass 
      energies $\sqrt{s}$ planned as well as to the coverage of existing nuclear neutral- and
      charged-current DIS measurements.
      %
      Bins with less than 30 events have been excluded.
      %
      \textcolor{red}{(To be replaced once AdvSND and new fluxes are available.)}
      }
    \label{fig:Kin_nNNPDF30_EIC_FPF}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
